### 2023-01-26 documentation/paper.tex
FEATURE: Add images

%-------------------------------------------------------------------------
% uncomment for using teaser (comment if you don't want a teaser)
\teaser{
    \hspace{\fill}
    \includegraphics[width=0.9\linewidth]{images/ModelbasedTrackingExample.png}
    \hspace{\fill}
    \centering
    \caption{Best teaser image you can provide \ldots}
    \label{fig:teaser}
}

@@

\begin{enumerate}
    \item Burst capture: A sequence of raw images is captured. In contrast to the classic 
          multi-exposure approach, each image will be underexposed and all images have the
          same exposure. An image bursts consists of two to eight single images.
    \item Image alignment: The sharpest image of the first three images in the burst is 
          selected as reference image and the remaining images in the burst are aligned 
          to it. This corrects for any movement or misalignment between frames.
    \item Image merging: The aligned raw images are merged to create a single intermediate 
          raw image that will then be further processed.
    \item Finishing: The merged image undergoes a set of operations including general
          correction, demosaicking and tone mapping. The most important operation is
          dynamic range compression which reduces the contrast between light and dark
          areas while preserving local contrast. To do so, the local tone mapping method
          \textit{exposure fusion} was used, which blends together the best parts of
          differently exposed images. As there is only one merged image left, the ones 
          to blend are created synthetically from the merged image.

\end{enumerate}

@@

@@

%-------------------------------------------------------------------------
\section{Acknowledgements}
\label{sec:acknowledgements}
\begin{itemize}
      \item Cat
      \item Elementary school teacher
      \item Ex girlfriend
      \item Random dude at the bar who bought a round
\end{itemize}

>>>>

%-------------------------------------------------------------------------
% uncomment for using teaser (comment if you don't want a teaser)
\teaser{
    \hspace{\fill}
    \includegraphics[width=0.9\linewidth]{images/teaser.png}
    \hspace{\fill}
    \centering
    \caption{
      Left images: Sample from a image burst captured with a Sony Alpha A6000 camera
                   with focal length $18mm$, shutter speed $1/50s$, ISO $400$ 
                   and aperture $f/4.0$ in a low light situation.
      Right image: Processed burst images with settings gain $g = 1.2$ and dynamic 
                   range compression $c = 3.0$.
    }
    \label{fig:teaser}
}

@@

\begin{enumerate}
    \item Burst capture: A sequence of raw images is captured. In contrast to the classic 
          multi-exposure approach, each image will be underexposed and all images have the
          same exposure. An image burst consists of two to eight single images.
    \item Image alignment: The sharpest image of the first three images in the burst is 
          selected as reference image and the remaining images in the burst are aligned 
          to it. This corrects for any movement or misalignment between frames.
    \item Image merging: The aligned raw images are merged to create a single intermediate 
          raw image that will then be further processed.
    \item Finishing: The merged image undergoes a set of operations including general
          correction, demosaicking and tone mapping. The most important operation is
          dynamic range compression which reduces the contrast between light and dark
          areas while preserving local contrast. To do so, the local tone mapping method
          \textit{exposure fusion} was used, which blends together the best parts of
          differently exposed images. As there is only one merged image left, the ones 
          to blend are created synthetically from the merged image.
\end{enumerate}

@@

\subsection{Noisy low light situations}

\begin{figure}
      \hspace{\fill}
      \includegraphics[width=0.9\linewidth]{images/noise.png}
      \hspace{\fill}
      \centering
      \caption{
            Left images: Noisy low light sample from bursts provided by the supplemental dataset
            to \cite{Hasinoff2016burst}. Top row shows full image while bottom shows zoom in noisy
            area.
            Right images: Processed burst images with settings gain $g=1.0$ and dynamic 
            range compression $c=2.5$.
      }
      \label{fig:noise}
\end{figure}

To find out how the HDR+ implementation handles images containing high noise, several 
image bursts with high noise were processed. As can be seen in \cref{fig:noise}, the noise was 
removed very well in all examples. Even when zooming in, hardly any noise is visible 
compared to the original image.  The results were all obtained with the same starting 
parameters and were satisfactory throughout.

\subsection{Low contrast or dynamic range situations}

\begin{figure}
      \hspace{\fill}
      \includegraphics[width=0.9\linewidth]{images/contrast_burst.png}
      \hspace{\fill}
      \centering
      \caption{
            Left images: Low contrast sample from bursts provided by the supplemental dataset
            to \cite{Hasinoff2016burst}.
            Right images: Processed burst images with settings gain g and dynamic 
            range compression c from top to bottom image: $g=1.0$, $c=2.5$ | $g=1.0$, $c=1.5$ | $g=1.0$, $c=1.5$.
      }
      \label{fig:contrast}
\end{figure}

\cref{fig:contrast}

\subsection{Moving objects}

\begin{figure*}
      \hspace{\fill}
      \includegraphics[width=0.9\linewidth]{images/moving_burst.png}
      \hspace{\fill}
      \centering
      \caption{Low light image capture of moving objects}
      \label{fig:moving}
\end{figure*}

\begin{figure}
      \hspace{\fill}
      \includegraphics[width=0.9\linewidth]{images/ghosting.png}
      \hspace{\fill}
      \centering
      \caption{Detail of \cref{fig:moving} showing ghosting }
      \label{fig:ghosting}
\end{figure}

\cref{fig:moving}
\cref{fig:ghosting}

@@

%-------------------------------------------------------------------------
\section{Acknowledgements}
\label{sec:acknowledgements}
\begin{itemize}
      \item Cat
      \item Elementary school teacher5
      \item Random dude at the bar who bought a round
\end{itemize}
